Creating Venn diagrams

### 2020-04-29 Scripts_for_results/08_creating_venn_diagrams.Rmd
initial commit

---
title: "Creating enriched heatmaps"
author: "Spiro Stilianoudakis"
date: "4/29/2020"
output: html_document
---

@@

## Enriched heatmap function

```{r}
enriched_func <- function(boundaries, annotations, e=5, w=50, ct){
  axis_names <- c(paste0("-",e,"kb"), "Center", paste0(e,"kb"))

  norm_mat <- normalizeToMatrix(annotations, 
                                boundaries, 
                                value_column = "coverage", 
                                extend = e*1000, 
                                w = 50,
                                mean_mode = "w0",
                                keep = c(0,.999))
  EH <- EnrichedHeatmap(norm_mat, 
                        col = ifelse(ct=="ARROWHEAD" | ct=="PEAKACHU" | ct=="LOLLIPOP", c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)),
                                     c("black",colorRampPalette(c("white", "pink", "red"))(99))), 
                        #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                        row_title="Boundaries",
                        show_heatmap_legend = FALSE,
                        row_title_side="left", 
                        column_title=ct, 
                        axis_name = axis_names,
                        column_title_gp = gpar(fontsize = 10),
                        row_title_gp = gpar(fontsize = 10),
                        axis_name_gp = gpar(fontsize = 10),
                        top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = ifelse(ct=="ARROWHEAD", "blue", "red"), 
                                                                                           fontsize = 10,
                                                                                           lwd = 2), 
                                                                                 axis_param = list(side = "right",
                                                                                                   facing = "inside"))))
  return(EH)
}

@@

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

@@

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

@@

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

@@

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

@@

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

@@

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

@@

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

@@

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

@@

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

@@

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```

###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```

###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```

###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

>>>>

---
title: "Creating Venn diagrams"
author: "Spiro Stilianoudakis"
date: "4/29/2020"
output: html_document
---

@@

@@

@@

all_true_bounds_gm12878 <- do.call("c", true_bound_list)
all_pred_bounds_gm12878 <- do.call("c", pred_bound_list)

all_true_bounds_gm12878 <- flank(all_true_bounds_gm12878, 5000, both=TRUE)
all_pred_bounds_gm12878 <- flank(all_pred_bounds_gm12878, 5000, both=TRUE)

@@

@@

@@

all_true_bounds_k562 <- do.call("c", true_bound_list)
all_pred_bounds_k562 <- do.call("c", pred_bound_list)

all_true_bounds_k562 <- flank(all_true_bounds_k562, 5000, both=TRUE)
all_pred_bounds_k562 <- flank(all_pred_bounds_k562, 5000, both=TRUE)

@@

### Within cell line (preciseTAD vs ARROWHEAD)

```{r}
venn_cnt2venn <- function(venn_cnt){
  n <- which(colnames(venn_cnt)=="Counts") - 1
  SetNames=colnames(venn_cnt)[1:n]
  Weight=venn_cnt[,"Counts"]
  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
  Venn(SetNames=SetNames, Weight=Weight)
}

###### GM12878

res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
                                  all_true_bounds_gm12878),
                       NameOfPeaks=c("preciseTAD", "ARROWHEAD"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

###### K562

res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562,
                                  all_true_bounds_k562),
                       NameOfPeaks=c("preciseTAD", "ARROWHEAD"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

#### Across cell line

```{r}
###### preciseTAD

res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
                                  all_pred_bounds_k562),
                       NameOfPeaks=c("GM12878", "K562"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

###### ARROWHEAD

res <- makeVennDiagram(Peaks=list(all_true_bounds_gm12878,
                                  all_true_bounds_k562),
                       NameOfPeaks=c("GM12878", "K562"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

@@

@@

### Within cell line (preciseTAD vs PEAKACHU)

```{r}
venn_cnt2venn <- function(venn_cnt){
  n <- which(colnames(venn_cnt)=="Counts") - 1
  SetNames=colnames(venn_cnt)[1:n]
  Weight=venn_cnt[,"Counts"]
  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
  Venn(SetNames=SetNames, Weight=Weight)
}

###### GM12878

res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
                                  all_true_bounds_gm12878),
                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

###### K562

res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562,
                                  all_true_bounds_k562),
                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

#### Across cell line

```{r}
###### preciseTAD

res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
                                  all_pred_bounds_k562),
                       NameOfPeaks=c("GM12878", "K562"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

###### PEAKACHU

res <- makeVennDiagram(Peaks=list(all_true_bounds_gm12878,
                                  all_true_bounds_k562),
                       NameOfPeaks=c("GM12878", "K562"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

@@

@@

### Within cell line (preciseTAD vs LOLLIPOP)

```{r}
venn_cnt2venn <- function(venn_cnt){
  n <- which(colnames(venn_cnt)=="Counts") - 1
  SetNames=colnames(venn_cnt)[1:n]
  Weight=venn_cnt[,"Counts"]
  names(Weight) <- apply(venn_cnt[,1:n], 1, paste, collapse="")
  Venn(SetNames=SetNames, Weight=Weight)
}

###### GM12878

res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
                                  all_true_bounds_gm12878),
                       NameOfPeaks=c("preciseTAD", "LOLLIPOP"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

###### K562

res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562,
                                  all_true_bounds_k562),
                       NameOfPeaks=c("preciseTAD", "LOLLIPOP"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

#### Across cell line

```{r}
###### preciseTAD

res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
                                  all_pred_bounds_k562),
                       NameOfPeaks=c("GM12878", "K562"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))

###### LOLLIPOP

res <- makeVennDiagram(Peaks=list(all_true_bounds_gm12878,
                                  all_true_bounds_k562),
                       NameOfPeaks=c("GM12878", "K562"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn.pt, gp = gp, show=list(Universe=FALSE))), top=textGrob("", gp=gpar(fontsize=50)))
